Assessing United States county-level exposure for tropical cyclone impact research

### 2020-07-12 ehp_revision/response_to_reviewers.Rmd

\textit{Lines 185--187 from original manuscript:}

\begin{quotation}
\noindent
\textit{"We used tracking data from HURDAT2, which records the storm center’s
position at the synoptic times of 6:00 am, 12:00 pm, 6:00 pm, and 12:00 am
Coordinated Universal Time (UTC)."}
\end{quotation}
\end{shaded}

**Response:**

"Synoptic meteorology" refers to ...
A key idea is that observations from a widespread geographical area can be
integrate to provide a picture of large-scale weather [features?], including
large areas of high or low pressure [?].

> "In meteorology, the term synoptic denotes simultaneous observations taken
globally, or at least over a large area." [@willoughby2007hurricane]

> "Nearly 20 years ago [from 1937] [Bjerknes] declared that numerous and 
important problems might be solved with the aid of observations already 
assembled in the archives of different bureaus, but that the difficulties
in making these observations serve a special purpose were unsurmountable
for the individual scholar. He added that, in particular, the synoptic 
charts representing the momentary states of the atmosphere over large
areas of the earth, in all the necessary details and exactitude, were 
excessively difficult to assemble. His proposal was that there be entered
at the central bureau of each country, on the appropriate maps, all the available
observations taken in that country and that there be employed, by the different
bureaus, maps that may be superimposed or juxtaposed." [@gregg1937international]

However, to integrate data from many sources to provide inputs for broadscale,
synoptic analysis, it is helpful to use some standards in collecting these data
at different locations. To facilitate numerical weather forecasting and other
synoptic meteorology, weather data are regularly collected at standardized
times, so that the data can be more easily integrated as an input to models.
This practice extends back over 100 years, when data were collected from many
[offices?] in the US by telegram [?] at regular times during the day and used to
create synoptic weather maps that captured major weather systems in the country.

> "In order to allow comparison of surface conditions at the same time throughout 
the world, the groups regulating the collection of hydrometeorological data have
established a standard time for taking observations. These observations will have
times observed within the 10 minutes preceding the UTC standard time. Hence 
surface observations for meteorological use have timestamps reflecting 0000, 
0300, 0600, 0900, 1200, 1500, 1800, 2100 UTC." [@usnwstime]

> "Since the end of World War II, observers have launched rawinsonde observation
worldwide at 00 and 12 UTC (coordinated universal time). High-threat situations, 
such as impending TC landfall, may dictate observations at 6-h or even 3-h intervals. 
Interpolating rawinsonde observations to the model's mesh and starting the calculation
at a synoptic time is the simplest way to prepare a model initial condition."
[@willoughby2007hurricane]

> "Because simple interpolation in space and time is a less-than-optimum way to 
use observations, nonsynoptic data require elaborate four-dimensional variational
data assimilation schemes." [@willoughby2007hurricane]

> "By 1941, charts for the 750, 500, and 250 mbar surfaces were being prepared daily
for 0400, 1200, and 2000 GMT." [@grahame2000development]

> "During the period considered here, NHC issued advisories 3 h after the standard
synoptic time (0300, 0900, 1500, and 2100 UTC)." [@torn2012uncertainty]

> "The operation data assimilation and forecast cycle interval is 6 h" [@aberson201010]

> "Dan Petersen asked whether a data deficiency really exists with all the 
observational sources in the Atlantic region, or are the data not being
properly used in the numerical models? ... Steve Lord emphasized the difficulty of the 
task because many of these observations are not obtained at the synoptic times..."
[@elsberry1992there]

> "In the modern era, forecasters rely on purely dynamical models that integrate the 
Navier-Stokes equations for atmospheric motions to represent both the storm itself and
its surroundings. Numerical models are structured on a computational grid with 
temperature, moisture, and wind tabulated in more-or-less rectangular cells." 
[@willoughby2007hurricane]

> "Predicting the weather required a widespread but highly coordinated team of 
observers and forecasters. Organization was key... They transmitted data from the 
field using forms and protocols adapted from those that Abbe had developed while 
forecasting the weather from Cincinnati, Ohio. The information arrived by telegraph
coded to maximize accuracy and minimize the word count and changes. The reports piled
up in a rush at the appointed hours." [@willis2006cleveland]

> "Three times daily the duty forecaster broadcast a synopsis of prevailing weather
conditions nationwide..." [@willis2006cleveland]

> "The requirement of synoptic data collection is easily met by the
'conventional' observing system now serving as the main source of meteorological 
data throughout the world, since it is based on human observations which could 
be scheduled at convenient synoptic times." [@morel1971initialization]

Since large-scale weather features are very larger, relevant data for a synoptic
map often comes from locations with different local times. The need for
synchronized weather data collection therefore actually played an important role
in establishing standardized time zones in the United States in [year]. Synoptic
weather times are typically set based on the Universal Time Constant, with times 
recorded in Coordinated Universal Time (i.e.,
Greenwich ...), and time stamps on weather maps and data based on this time zone
often is given a "Z" (for "Zulu", an earlier name for this timezone) after the
time.

> "Accuracy in forecasting depended on the accurate timing of observations. At
first weather observers used local time because no system of standard time
existed, either in the United States or abroad. Local time often meant railroad
time, and that could vary as much as 20 minutes from the time proper to the
local meridian. Abbe called for change, emphasizing the need for simultaneous
readings by Signal Service observers in order to construct accurate charts and
weather maps. In 1875, he recommended to the president of the American
Meteorological Society the establishment of a committee on standard time. ...
Abbe's report in 1879 recommended the system of meridians that is now in general
use ... a system of time meridians one hour apart across the country, anchored
on the Greenwich prime meridian." [@willis2006cleveland]

> "From Abbe's perspective, however, the full potential for dynamic weather
prediction would not be achieved without standard time worldwide."
[@willis2006cleveland]

> "The time in all hydrometeorological products is expressed according to 
a single standard, which is the Universal Coordinated Time (UTC) 
(formerly known as Greenwich Mean Time [GMT] or Zulu (zero) Time [Z])."
[@usnwstime]

> "The U.S. National Weather Service base all data and product times on the 
UTC standard. ... A common practice is to include a time of the observation 
or event denoting the time with a following capital letter 'Z' to indicate the 
time as UTC." [@usnwstime]

We have added text to clarify the meaning of "synoptic times" in the text:

> **Text in revised manuscript (relevant change in bold):**
"We used tracking data from HURDAT2, which records the storm center’s position
at **four standardized times for weather data collection (synoptic times),**
6:00 am, 12:00 pm, 6:00 pm, and 12:00 am Coordinated Universal Time (UTC)."

@@

\textit{Lines 294--295 from original manuscript:}

\begin{quotation}
\noindent
\textit{"The tornado observations from this dataset form a traditional tornado
event database for the US, and so we did not further validate the tornado event
data."}
\end{quotation}
\end{shaded}

**Response:**

The NOAA Storm Events database originated as a database for recording tornadoes
[? anything else] in the US in 195[x], and was originally called ... . The
database has gone through a number of expansions to cover more events, and it
now includes reports of other types of [hydrometeorological?] disaster events,
including floods, extreme heat and cold, wildfires, frost, hail, ... . However,
it has maintained its status as the database of record [?] for tornadoes in the
United States.

Examples of research papers that leverage this database as a record of tornado
events, or the version of it shared by the [Severe Storm ...] through their
website [ref], include ... .

[Is this database used to validate tornado forecasts / warnings?]

### 2020-07-12 ehp_revision/writing/ehp_methods.tex
Add in some on synoptic times

We first measured how close each storm's central track came to each county. We
used tracking data from \ac{HURDAT2}, which records the storm center's position
at the synoptic times of 6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC}.  We
interpolated this position to~15-\si{\minute} intervals using natural cubic
spline interpolation~\parencite{hurricaneexposure}. At each~15-\si{\minute}
interval, we measured the distance between the storm's center and each county's
population mean center~\parencite{countycenters}. We took
the minimum distance for each county as a measure of how close the storm came
to the county over its lifetime.  We also recorded the time when this occurred
for each county so we could later link observed data on precipitation,
flooding, and tornadoes.  To allow matching with data recorded in
local time (e.g., health data), we converted these times from \ac{UTC} to local
time~\parencite{countytimezones}.

>>>>

We first measured how close each storm's central track came to each county. We
used tracking data from \ac{HURDAT2}, which records the storm center's position
at four standardized times for weather data collection (synoptic times),
6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC}.  We interpolated this
position to~15-\si{\minute} intervals using natural cubic spline
interpolation~\parencite{hurricaneexposure}. At each~15-\si{\minute} interval,
we measured the distance between the storm's center and each county's
population mean center~\parencite{countycenters}. We took the minimum distance
for each county as a measure of how close the storm came to the county over its
lifetime.  We also recorded the time when this occurred for each county so we
could later link observed data on precipitation, flooding, and tornadoes.  To
allow matching with data recorded in local time (e.g., health data), we
converted these times from \ac{UTC} to local time~\parencite{countytimezones}.
